Concurrent Programming with CXL

### 2020-06-18 book/paper.tex
Latest version

@@

\section*{Exercises}
\begin{enumerate}
\item Figure~\ref{fig:csonebit} presents another correct solution to the
mutual exclusion problem.  It is similar to the one in
Figure~\ref{fig:upflags}, but has a process \emph{back out and try again}
if it finds that the other process is either trying to enter the critical
section or already has.  Compare this algorithm with Peterson's.  What are
the advantages and disadvantages?
\item A colleague of the author asked if the first two assignments in
Peterson's algorithm (setting \texttt{flags[self]})
to \texttt{True} and \texttt{turn} to \texttt{1 - self}) can be reversed.
After all, they are different variables assigned independent values---in a
sequential program one could surely swap the two assignments.
See if you can figure out for yourself if the two assignments can be
reversed.  Then run the program in Figure~\ref{fig:peterson} after reversing
the two assignments and describe in English what happens.
\item Bonus question:
Can you find an inductive invariant for Figure~\ref{fig:csonebit} to prove
it correct?
\item Bonus question:
Can you generalize Peterson's algorithm to more than two processes?
\end{enumerate}

>>>>

\section*{Exercises}
\begin{enumerate}
\item Figure~\ref{fig:csonebit} presents another correct solution to the
mutual exclusion problem.  It is similar to the one in
Figure~\ref{fig:upflags}, but has a process \emph{back out and try again}
if it finds that the other process is either trying to enter the critical
section or already has.  Compare this algorithm with Peterson's.  What are
the advantages and disadvantages?
\item
Can you find an inductive invariant for the algorithm in
Figure~\ref{fig:csonebit} to prove it correct?
Here's a pseudo-code version of the algorithm to help you.  Each line
is an atomic action:
\begin{code}
\begin{verbatim}
    initially: flagX = flagY = False

    process X:                          process Y:
        X0: flagX = True                   Y0: flagY = True
        X1: if not flagY goto X4           Y1: if not flagX goto Y4
        X2: flagX = False                  Y2: flagY = False
        X3: goto X0                        Y3: goto Y0
        X4: ...critical section...         Y4: ...critical section...
        X5: flagX = False                  Y5: flagY = False
\end{verbatim}
\end{code}
\item A colleague of the author asked if the first two assignments in
Peterson's algorithm (setting \texttt{flags[self]})
to \texttt{True} and \texttt{turn} to \texttt{1 - self}) can be reversed.
After all, they are different variables assigned independent values---in a
sequential program one could surely swap the two assignments.
See if you can figure out for yourself if the two assignments can be
reversed.  Then run the program in Figure~\ref{fig:peterson} after reversing
the two assignments and describe in English what happens.
\item Bonus question:
Can you generalize Peterson's algorithm to more than two processes?
\end{enumerate}

@@
